Abstract Binding Trees

### 2015-10-28 paper.tex
Try just papering over notation w/ a "remark"
@freebroccolo I wonder if this is fine? It got really gnarly-looking
when I tried to explicitly do the quantification.

@@

%% TODO: in the above, \vec{q} is a list of sorts, but we need to pick out symbol
%% names for these before we can extend \Upsilon! Or do we?

>>>>

\begin{remark}
  A \emph{relative monad} on a functor $\Of{J}{\mathbf{J}\to\mathbf{C}}$ is a
  monoid in the functor category $\mathbf{C}^\mathbf{J}$
  \cite{altenkirch-chapman-uustalu:2015}. A presheaf $A$ with a substitution
  monoidal structure $\Pair{\nu}{\varsigma}$ can be viewed as a relative monad
  on the presheaf $\Of{V}{\Sets^\Seq}$ of variables.
\end{remark}

@@

\begin{remark}
  By $\Upsilon,\vec{p}$ we mean any extension of $\Upsilon$ by fresh symbols $\vec{u}$ of sorts $\vec{p}$.
\end{remark}
